A discussion of the intersection of the kernels of each $(1+T_i)$ acting on $W_{2n+r}^r$

### 2019-07-29 tex/kernel_comments.tex
Low 2n+r transitions, readded kernel_comments, added action isotopy macro to milesMacros

  Fix some basis element $M\in W_{2n+r}^r$. Define $M(a):=b$ iff $a$ and $b$ are matched in $M$, $M(a):=a$ if $a$ is an anchor in $M$.
  {\color{magenta} Should specify that $a,b$ are integers $1 \leq a,b \leq 2n + r$.} 
  Given that $M$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $M(a,b)$ of $M$ to be the basis element $K\in W_{b-a+1}^{r'}$ specified by $K(i)=M(i+a-1)-a+1$. This sub-matching is defined for $a<b$ when $M(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$. See Figure 1.

  If $b\geq a$ and nodes $1\leq a,...,b\leq 2n+r$, $M(a,b)$ will still refer to those nodes, but will not be a sub-matching. For any other $a,b$, we define $M(a,b)$ to be an element of the representation with no nodes.
\end{definition}

@@

\newpage
\section{Defining the kernel for $e=n+r+1$}
In this section we will fully characterize $\cap\text{ker}(1+T_i)$ when $e=n+r+1$. We will prove that it is one dimensional and give a basis. Note that we still have not proved the kernel is trivial when $e$ divides but is not equal to $n+r+1$. That proof requires results from this section, and will come next section.

@@

@@

	Let $W_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$. Let $w\in\cap\text{ker}(1+T_i)$. WLOG the rainbow element $R$ has coordinate 1 in $w$ (by proposition 2.2).
	\\

@@

\end{proposition}

\vspace{5mm}
Before proving this proposition, it will be useful to clarify exactly what it states.

\vspace{5mm}
The first statement of this proposition says that, given an element of the kernel $w$, we can write the coordinate of any basis element $\beta$ in $w$ as a rational function of $q$ as long as $Q_1...Q_{n+r-1}\not=0$.

@@

	\item Finish the proof through induction.
\end{enumerate}

\vspace{10mm}
\begin{proof}
	Note that statement (i) was necessary to state (ii), but it is natural to prove both statements together, so this is how we will proceed.
	\\

	By proposition 2.2 the rainbow element has coordinate 1 in $w\in W_{2n+r}^r$. By proposition 2.3 the element $R_1:=R_{L,n+r-1}$ has coordinate $Q_{n+r-1}$ in $w$. Then $R_1(3,2n+r)$ is the rainbow element in  $W_{2(n-1)+r}^r$, so the element $R_2$ defined by $R_2(1,2)=R_1(1,2)$, $R_2(3,2n+r)=R_{L,n+r-2}\in W_{2(n-1)+r}^r$ has coordinate $Q_{n-1}Q_{n-2}$. Generally, define $R_i$ by $R_i(1,2(i-1))=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r)=R_{L,2n+r-i}$. Then the coefficient of $R_i$ is $Q_{n+r-1}...Q_{n+r-i}$. These elements are shown in figure 5.

@@

	Now, I claim that this method can be applied to any rainbow sub-matching in exactly the same way. In other words, extraneous nodes add no complexity to this argument.

@@

	To turn this into an inductive proof, suppose statements (i) and (ii) are true for all representations with $2n'+r'<2n+r$ nodes.

@@

	So, by induction, the proposition holds.

\vspace{5mm}
The following few corollaries will help to simplify some later proofs.

@@

	$$x_\beta(q)=x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}}=$$

@@

	This proves the inductive step, so with base case $j=1$ the corollary holds.

\vspace{5mm}
\begin{corollary}
	$\beta\in W_{2n+r}^r$, then $x_\beta(q)\not=0$ if $e>n+r$.
\end{corollary}

@@

\vspace{5mm}
\noindent\rule{16.5cm}{0.4pt}

@@

	\caption{In the first line we act under an arc, so if another element without that arc is sent to that element, it must fix the arc as shown in the second line. In the third line we act to the right of an anchor, so if another element without that anchor is sent to that element, it must fix the anchor as shown in the fourth line. 
	}
	%\label{Action}
\end{figure}

@@

\vspace{5mm}
\begin{lemma}
	Take a basis element $\beta\in W_{2n+r}^r$. Suppose the leftmost anchor in $\beta$ is at index $b$, or let $b=2n+r+1$ if there is no anchor. Define $a_j$ such that $\beta(a_j)=a_{j-1}+1$ and $\beta(a_1)=1$ for all $j$ such that $a_j<b$.

@@

\vspace{5mm}
Lastly, we will need a small combinatorial result.

\begin{lemma}
	Suppose $n>b\geq a>0$ and $e>n$. Then $$Q_{n-a}Q_b-Q_{n-b-1}Q_{a-1}=Q_{n}Q_{b-a}$$
\end{lemma}

\begin{proof}
	If $b=1$, the only possibility for $a$ is 1, in which reduces to lemma 2.4.

	Suppose the lemma is true for all $\tilde{b}<b+1$. Then for $a< b$ we have

	$$Q_{n-a}Q_b -Q_{n-b-1}Q_{a-1}=Q_{n}Q_{b-a}$$

	$$Q_1Q_{n-a}Q_b-Q_1Q_{n-b-1}Q_{a-1}=Q_1Q_{n}Q_{b-a}$$

	from lemma 2.4, we have

	$$Q_{n-a}(Q_{b+1}+Q_{b-1})-(Q_{n-b}+Q_{n-b-2})Q_{a-1}=Q_{n}(Q_{b-a-1}+Q_{b-a+1})$$

	and from the inductive hypothesis we have

	$$Q_{n-a}Q_{b+1}-Q_{n-b}Q_{a-1}=Q_{n}Q_{b-a+1}$$

	as desired.

	For $a=b$ we have

	$$Q_{n-b}Q_b -Q_{n-b-1}Q_{b-1}=Q_{n}$$

	$$Q_1Q_{n-b}Q_b-Q_1Q_{n-b-1}Q_{b-1}=Q_1Q_{n}$$

	from lemma 2.4, we have

	$$Q_{n-b}(Q_{b+1}+Q_{b-1})-(Q_{n-b}+Q_{n-b-2})Q_{b-1}=Q_1Q_{n}$$

	$$Q_{n-b}Q_{b+1}-Q_{n-b-2}Q_{b-1}=Q_1Q_{n}$$

	as desired.

	For $a=b+1$, we continue:

	$$Q_1Q_{n-b}Q_{b+1}-Q_1Q_{n-b-2}Q_{b-1}=Q_1Q_1Q_{n}$$

	$$(Q_{n-b-1}+Q_{n-b+1})Q_{b+1}-Q_{n-b-2}(Q_{b}+Q_{b-2})=(1+Q_2)Q_{n}$$

	So by the inductive hypothesis

	$$Q_{n-b-1}Q_{b+1}-Q_{n-b-2}Q_{b}=Q_{n}$$

	as desired, and the proof is finished by induction.

@@

	\vspace{5mm}
	To prove the inductive step for both (i) and (ii), we must split into cases. Note that if $E_\beta$ is defined to be the pre-image of $\beta$ under the action of $(1+T_i)$, $E_{\beta(a,b)}$ is defined to be the pre-image of $\beta(a,b)$ under action of $(1+T_{i-a+1})$:

	\begin{enumerate}
	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, and that $\exists s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\beta(s)=t$. Also suppose the leftmost anchor is at some index $u>t$, or that there are no anchors. Then we have a sub-matching $\beta(s,t)$, and by lemma 3.6 $E_\beta\subset Y_\beta$. Then, using corollary 3.2, the following equality holds:

@@

	\vspace{5mm}
	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, the leftmost anchor is at a position $u>i+1$ or there are no anchors, and $\not\exists s,t$ such that $\beta(s)=t$ and $s<i<t-1$. Lemma $3.7$ characterizes all $\alpha\in E_\beta$. We would like to prove the following for arbitrary $q$ where $e>n+r$:

@@

	See figure 9 for an example of this equality. Note that if $e=n+r+1$, $Q_{n+r}$ is the only zero component in the right side of this equation, so proving this equation is sufficient to prove case three.
	\\

	We will prove this equality through yet another inductive proof, this time inducting on the number of top level humps, including the leftmost anchor.

	Formally, as we have in earlier lemmas, we will define $a_j$ by $a_1:=\beta(1)$, $a_j:=\beta(a_{j-1}+1)$. Then define $b_\beta$ such that $a_{b_\beta}=u$ if there is an anchor or $a_{b_\beta}=2n+r$ otherwise. We induct on $b_\beta$.
	\\

	If $b_\beta=1$, we must be in $W_2^0$ to be in case 3 (otherwise $s<i<t-1$ for some $s,t$ where $\beta(s)=t$), which is trivially satisfied. 
	\\

%	For our base case we will prove $b=2$. This means either $a_1+1$ is an anchor, or $\beta(a_1+1)=2n+r$. 
%	\\
%	
%	First base case:
%	
%	If $a_1+1$ is an anchor, to still be in case 3 we must have $i=1$ and $a_1=2$. In this case, lemma 3.7 gives that there is only one element in $E_\beta$, and that element is $\alpha$ defined by $\alpha(4,2n+r)=\beta(4,2n+r)$, $\alpha(1)=1$, and $\alpha(2)=3$. Then $x_\beta=Q_{n+r-1}x_\beta(3,2n+r)=Q_{n+r-1}\beta(4,2n+r)$ and $x_\alpha=x_{\alpha(2,2n+r)}=Q_{n+r-2}x_{\beta(4,2n+r)}$. So, using lemma 2.4, we have $(q+1)x_\beta(q)+q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(4,2n+4)}(q)Q_{n+r}$ as desired.
%	\\
%	
%	Second base case: 
%	
%	If $\beta(a_1+1)=2n+r$, to be in case 3 we need either $a_1=2$ or $a_1=2n+r-2$. In both cases lemma 3.7 gives only one element $\alpha$ in $E_\beta$. In the first case $x_\beta=Q_{n+r-1}x_{\beta(3,2n+r)}=Q_{n+r-1}x_{\beta(4,2n+r-1)}$, and $x_\alpha=x_{\alpha(2,2n+r-1)}=Q_{n+r-2}x_{\beta(4,2n+r-1)}$ so again using lemma 2.4 $(q+1)x_\beta(q)+q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(4,2n+r)}(q)Q_{n+r}$ as desired. In the second case $x_\beta=\frac{Q_{n+r-1}...Q_{1}}{Q_1...Q_{n+r-2}}x_{\beta(2,2n+r-3)}=Q_{n+r-1}x_{\beta(2,2n+r-3)}$, and, using corollary 3.3, $x_\alpha=\frac{Q_{n+r-2}...Q_{1}}{Q_1...Q_{n+r-3}}x_{\alpha(2,2n+r-3)}=Q_{n+r-2}x_{\beta(2,2n+r-3)}$, so again using lemma 2.4, we have $(q+1)x_\beta(q)+q^{1/2}x_\alpha(q)=-q^{1/2}x_{\beta(1,2n+r-2)}(q)Q_{n+r}$ as desired, and all base cases are proved.
%	\\

	Suppose for all basis elements $\alpha$ such that $b_\alpha<b_\beta$, the equality holds. Suppose $i\not=1$. Then $a_1<i$ and lemma 3.7 gives that there is a unique $\upsilon\in E_\beta$ such that $\upsilon(1)\not=a_1$. Thus we have the following equality:

	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$

	$$(x_{\beta(1,a_1)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}})((1+q)x_{\beta(a_1+1,2n+r)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_{\alpha(a_1+1,2n+r)}(q))$$

	Define $Y_\beta$ as before with respect to the sub-matching $\beta(a_1+1,2n+r)$. Then $\alpha\in E_\beta$, $\alpha\not=\upsilon$ implies $\alpha\in Y_\beta$. By our inductive hypothesis, we have that 
	$$(1+q)x_{\beta(a_1+1,2n+r)}(q)+\sum_{\alpha\in E_{\beta(a_1+1,2n+r)},\alpha\not=\beta(a_1+1,2n+r)}q^{1/2}x_{\alpha}(q)=$$
	$$
	-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}}$$

	By lemma 3.5, $\alpha\subset Y_\beta$, $\alpha\in E_\beta$ if and only if $\alpha(a_1+1,2n+r)\in E_{\beta(a_1+1,2n+r)}$. This implies:

	$$(1+q)x_{\beta(a_1+1,2n+r)}(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_{\alpha(a_1+1,2n+r)}(q)=$$

	$$-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}}$$

	So, combining with the aforementioned equality, we have

	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$

	$$(x_{\beta(1,a_1)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}})(-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}})=$$

	$$(x_{\beta(1,a_1)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}})(-q^{1/2}x_{\beta(a_1+1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-a_1/2}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1-a_1)/2}})(\frac{Q_{(i-1)/2-1}...Q_{(i-1-a_1)/2}}{Q_{(i-1)/2-1}...Q_{(i-1-a_1)/2}})=$$

	$$-q^{1/2}x_{\beta(1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}(\frac{Q_{n+r-a_1/2}Q_{(i-1)/2}}{Q_{(i-1-a_1)/2}})$$
	\\

	Separately, note that $\upsilon$ is defined by $\upsilon(2,a_1-1)=\beta(2,a_1-1)$, $\upsilon(a_1+1,i-1)=\beta(a_1+1,i-1)$, $\upsilon(i+2,2n+r)=\beta(i+2,2n+r)$, and $\upsilon(1)=i+1$, $\upsilon(a_1)=i$. Thus we may determine $x_\upsilon$, again utilizing corollary 3.2:

	$$x_\upsilon=x_{\beta(i+2,2n+r)}x_{\upsilon(2,i)}\frac{Q_{n+r-1}...Q_{n+r-(i+1)/2}}{Q_1...Q_{(i-1)/2}}=$$

	$$x_{\beta(i+2,2n+r)}(x_{\beta(2,a_1-1)}x_{\upsilon(a_1,i)}\frac{Q_{(i-1)/2-1}...Q_{(i-1)/2-(a_1-2)/2}}{Q_1...Q_{(a_1-2)/2-1}})\frac{Q_{n+r-1}...Q_{n+r-(i+1)/2}}{Q_1...Q_{(i-1)/2}}=$$

	$$x_{\beta(i+2,2n+r)}(x_{\beta(1,a_1)}x_{\beta(a_1+1,i-1)}\frac{Q_{(i-1)/2-1}...Q_{(i-1)/2-(a_1-2)/2}}{Q_1...Q_{(a_1-2)/2-1}})\frac{Q_{n+r-1}...Q_{n+r-(i+1)/2}}{Q_1...Q_{(i-1)/2}}=$$

	$$x_{\beta(i+2,2n+r)}x_{\beta(1,i-1)}\frac{Q_{n+r-1}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}(\frac{Q_{n+r-(i+1)/2}Q_{a_1/2-1}}{Q_{(i-1-a_1)/2}})$$
	\\

	Adding this into our previous equation, we have:

	$$-q^{1/2}x_{\beta(1,i-1)}(q)x_{\beta(i+2,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-(i-1)/2}}{Q_1...Q_{(i-1)/2}}(\frac{Q_{n+r-a_1/2}Q_{(i-1)/2}-Q_{n+r-(i+1)/2}Q_{a_1/2-1}}{Q_{(i-1-a_1)/2}})$$

	Applying lemma 3.8 to the portion of the equation above in parenthesis, the above is equivalent to

	as desired. Note that if $e\geq n+r+1$ the only term above that can be zero is $Q_{n+r}$ (by corollary 3.3). Thus we have proved the inductive step for the case where $i\not=1$.

	\vspace{5mm}
	If $i=1$, we instead look at the sub-matchings $\beta(1,a_{(b_\beta-1)})$, $\beta(a_{(b_\beta-1)}+1,2n+r)$. Again lemma 3.7 gives that there is a unique $\upsilon\in E_\beta$ such that $\upsilon(a_{(b_\beta-1)}+1)\not=\beta(a_{(b_\beta-1)}+1)$. Taking $Y_\beta$ with respect to the sub-matching $\beta(a_{(b_\beta-1)}+1,a_{b_\beta})$ again we have that $\alpha\in E_\beta$, $\alpha\not=\upsilon$ implies $\alpha\in Y_\beta$. Thus, following the same logic as before, we arrive at the following equality:

	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$

	$$(x_{\beta(a_{(b_\beta-1)}+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}})(-q^{1/2}x_{\beta(3,a_{(b_\beta-1)})}(q)Q_{a_{(b_\beta-1)}/2})=$$

	$$-q^{1/2}x_{\beta(3,2n+r)}\frac{Q_{n+r-1}Q_{a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$
	\\

	Again, we know the structure of $\upsilon$ from lemma 3.7. Suppose for now that $a_{b_\beta}$ is not an anchor, so it is $2n+r$. Then $\upsilon$ is defined by $\upsilon(3,a_{(b_\beta-1)})=\beta(3,a_{(b_\beta-1)})$, $\upsilon(a_{(b_\beta-1)}+2,2n+r-1)=\beta(a_{(b_\beta-1)}+2,2n+r-1)$, and $\upsilon(1)=2n+r$, $\upsilon(2)=a_{(b_\beta-1)}+1$. So we may again find $x_\upsilon$:

	$$x_\upsilon=x_{\upsilon(2,2n+r-1)}=x_{\beta(3,a_{(b_\beta-1)})}x_{\beta(a_{(b_\beta-1)}+2,2n+r-1)}\frac{Q_{n+r-2}...Q_{n+r-1-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}}=$$

	$$x_{\beta(3,a_{(b_\beta-1)})}x_{\beta(a_{(b_\beta-1)}+1,2n+r)}\frac{Q_{n+r-2}...Q_{n+r-1-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}}=x_{\beta(3,2n+r)}\frac{Q_{n-r-1-a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$

	Alternatively, if $a_{b_\beta}$ is an anchor, the definition of $\upsilon$ is now $\upsilon(3,a_{b_\beta}-1)=\beta(3,a_{b_\beta}-1)$, $\upsilon(a_{b_\beta}+1,2n+r)=\beta(a_{b_\beta}+1,2n+r)$, and $\upsilon(1)=1$, $\upsilon(2)=a_{b_\beta}$, so we have:

	$$x_\upsilon=x_{\upsilon(2,2n+r)}=x_{\beta(3,a_{(b_\beta-1)})}x_{\beta(a_{b_\beta}+1,2n+r)}\frac{Q_{n+r-2}...Q_{n+r-1-a_{(b_\beta-1)}/2}}{Q_1...Q_{a_{(b_\beta-1)}/2-1}}=x_{\beta(3,2n+r)}\frac{Q_{n-r-1-a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$

	so for our purposes $x_\upsilon$ is the same in either case.

	Incorporating into the above equation, we have:

	$$-q^{1/2}x_{\beta(3,2n+r)}\frac{Q_{n+r-1}Q_{a_{(b_\beta-1)}/2}-Q_{n-r-1-a_{(b_\beta-1)}/2}}{Q_{a_{(b_\beta-1)}/2-1}}$$

	By lemma 3.8, this is simply $-q^{1/2}x_{\beta(3,2n+r)}Q_{n+r}$ as desired, and we have finished proving case 3.
	\\

	\item The only cases we have not yet dealt with are those where either $1$ is an anchor or $\beta(1)=2n+r$. These are those cases related to our inductive hypothesis (ii).

	To not be in case 1 or 2, we must have that there are no anchors between index 1 and $i$, and that there is no integer $s$ such that $1<s<i<\beta(s)-1$. It follows from the same argument that proved lemma 3.6 that there exists exactly one $\upsilon\in E_\beta$ such that $\upsilon(1)\not=\beta(1)$. Define $N$ to be $2n+r$ if 1 is an anchor, or $2n+r-1$ if 1 is not an anchor. Then, defining $Y_\beta$ with respect to the sub-matching $\beta(2,N)$, we have that $\alpha\in E_\beta, \alpha\not=\upsilon$ if and only if $\alpha(2,N)\in E_{\beta(2,N)}$. Note that for $E_{\beta(2,N)}$ we may apply the inductive hypothesis from case 3, so we have:

	$$(1+q)x_\beta(q)+\sum_{\alpha\in E_\beta,\alpha\not=\beta,\upsilon}q^{1/2}x_\alpha(q)=$$

	$$(1+q)x_{\beta(2,N)}(q)+\sum_{\alpha\in E_{\beta(2,N)},\alpha\not=\beta(2,N)}q^{1/2}x_{\alpha}(q)=$$

	$$-q^{1/2}x_{\beta(2,i-1)}x_{\beta(i+2,N)}\frac{Q_{n+r-1}...Q_{n+r-i/2}}{Q_1...Q_{(i/2-1}}$$

	As in case 3, we can also determine $x_\upsilon$. $\upsilon$ is defined by $\upsilon(2,i-1)=\beta(2,i-1)$, $\upsilon(i+2,N)=\beta(i+2,N)$, $\upsilon(1)=i$, and $\upsilon(i+1)=2n+r$ if 1 is not an anchor or $i+1$ if 1 is an anchor, and we have:

	$$x_\upsilon=x_{\beta(2,i-1)}x_{\upsilon(i+2,N)}\frac{Q_{n+r-1}...Q_{n+r-i/2}}{Q_1...Q_{i/2-1}}$$

	Thus we have

	$$-q^{1/2}x_{\beta(2,i-1)}x_{\beta(i+2,N)}\frac{Q_{n+r-1}...Q_{n+r-i/2}}{Q_1...Q_{(i/2-1}}(1-1)=0$$

	as desired, and the last case is proved.
	\end{enumerate}

It should be noted that the induction for all of the above cases are codependent, but they only depend on the inductive hypotheses for $2n'+r'<2n+r$. So, since our base case holds for all the cases that apply to it, induction holds and the proposition is proved.

\begin{corollary}
	If $e=n+r+1$, $W_{2n+r}^r$ is reducible, and has a unique sign subrepresentation.
\end{corollary}

>>>>

  Fix some basis element $M\in W_{2n+r}^r$. Define $M(a):=b$ iff $a$ and $b$ are matched in $M$, $M(a):=a$ if $a$ is an anchor in $M$.
  {\color{magenta} Should specify that $a,b$ are integers $1 \leq a,b \leq 2n + r$.} 
  Given that $M$ has $r'$ anchors in the range $a,..,b$, define a \textbf{sub-matching} $M(a,b)$ of $M$ to be the basis element $K\in W_{b-a+1}^{r'}$ specified by $K(i)=M(i+a-1)-a+1$. This sub-matching is defined for $a<b$ when $M(i)\in \{a,a+1,...,b\}$ for all $i\in \{a,a+1,...,b\}$. See Figure 1.
\end{definition}

@@

\newpage
\section{Defining the kernel for $e=n+r+1$}
{\color{magenta} This is more of a thing to discuss when integrating into the draft, but this needs to be restructured in order to fit in.}
In this section we will fully characterize $\cap\text{ker}(1+T_i)$ when $e=n+r+1$. We will prove that it is one dimensional and give a basis. Note that we still have not proved the kernel is trivial when $e$ divides but is not equal to $n+r+1$. That proof requires results from this section, and will come next section.

@@

{\color{magenta} May just be a me thing, but I find the amount of vspace and the centering on the proposition statements to be visually confusing.}

@@

  Let $W_{2n+r}^r$ be a crossingless matchings representation, and suppose $Q_1,...Q_{n+r-1},\not=0$. Let $w\in\cap\text{ker}(1+T_i)$. WLOG {\color{magenta} assume} the rainbow element $R$ has coordinate 1 in $w$ (by proposition 2.2).
	\\

@@

\end{proposition}
{\color{magenta} This may be a stylistic thing, but the phrase ``I claim'' in a written proof feels weird to me.}
\vspace{5mm}
Before proving this proposition, it will be useful to clarify exactly what it states.

{\color{magenta} I'm not going to mention it again, but this vspacing is visually confusing to me.
I've been meaning to bring this up because I'm not exactly sure how to use this;
I generally use it sparingly (not often and $\leq$ line height) to separate large chunks in proofs.
It's fair if you like it this way, but I'd be a bit confused reading this.}

\vspace{5mm}
The first statement of this proposition says that, given an element of the kernel $w$, we can write the coordinate of any basis element $\beta$ in $w$ as a rational function of $q$ as long as $Q_1...Q_{n+r-1}\not=0$.
{\color{magenta} Is this a bit redundant? This just seems like the whole statement.}

@@

	\item Finish the proof through induction.
\end{enumerate}
{\color{magenta} I feel this would be better in a paragraph than an enumerated list;
it isn't complicated enough that a list really does anything but give an informal tone IMO.}
\vspace{10mm}
\begin{proof}
	Note that statement (i) was necessary to state (ii), but it is natural to prove both statements together, so this is how we will proceed.
	\\

	By proposition 2.2 the rainbow element has coordinate 1 in $w\in W_{2n+r}^r$. 
  {\color{magenta} Wasn't this already stated in the proposition?}
  By proposition 2.3 the element $R_1:=R_{L,n+r-1}$ has coordinate $Q_{n+r-1}$ in $w$. Then $R_1(3,2n+r)$ is the rainbow element in  $W_{2(n-1)+r}^r$, so the element $R_2$ defined by $R_2(1,2)=R_1(1,2)$, $R_2(3,2n+r)=R_{L,n+r-2}\in W_{2(n-1)+r}^r$ has coordinate $Q_{n-1}Q_{n-2}$. 
  {\color{magenta} the element $R_2$ defined by submatchings $R_2(1,2) := R_1(1,2)$ and $R_2(3,2n + r) := $\dots}
  Generally, define $R_i$ by $R_i(1,2(i-1))=R_{i-1}(1,2(i-1))$, $R_i(2i-1,2n+r)=R_{L,2n+r-i}$. Then the coefficient of $R_i$ is $Q_{n+r-1}...Q_{n+r-i}$. These elements are shown in figure 5.

@@

	Now, I claim that this method can be applied to any rainbow sub-matching in exactly the same way. In other words, extraneous nodes add no complexity to this argument.
  {\color{magenta} If it is significant enough to be stated as ``I claim'', it may be better put in the claim* environment, or as a lemma.}

@@

  {\color{magenta} Suppose inductively that\dots}
  To turn this into an inductive proof, suppose statements (i) and (ii) are true for all representations with $2n'+r'<2n+r$ nodes.

@@

	So, by induction, the proposition holds.
  {\color{magenta} Two comments on the inductive arument:
    \begin{enumerate}
      \item IMO inductive arguments flow better when they begin with the base case.
      \item I don't think that the verbose treatment of the induction argument is necessary or helpful;
        one actually needs to use the word induction once.
        I think a good structure is ``We will prove indutively that \dots For the base case $2n + r = 2$ \dots suppose \textit{indutive hypothesis}\dots qed'', which doesn't require one to remind the reader that they're reading an inductive argument.
    \end{enumerate}
}
\end{proof}

{\color{magenta} I do like this proof above, and I like the clear sectioning.
I think it might even be nice to see a \textit{Step n} at the beginning of each step as well as a small vspace for separation.}

\vspace{5mm}
The following few corollaries will help to simplify some later proofs.
{\color{magenta} ``some later arguments'' (``proofs'' feels like it breaks the tone).}

@@

  {\color{magenta} the align* environment would help this a lot.}
	$$x_\beta(q)=x_{\beta(1,a_1)}(q)x_{\beta(a_1+1,2n+r)}(q)\frac{Q_{n+r-1}...Q_{n+r-a_1/2}}{Q_1...Q_{a_1/2-1}}=$$

@@

	This proves the inductive step, so with base case $j=1$ the corollary holds.
  {\color{magenta} I don't think this needs to be said.}
\end{proof}

\vspace{5mm}
\begin{corollary}
  {\color{magenta} if $\beta \in W_{2n + r}^r$ is a basis element\dots} $\beta\in W_{2n+r}^r$, then $x_\beta(q)\not=0$ if $e>n+r$.
\end{corollary}

@@

{\color{magenta} I like this section a lot, and especially how the argument unfolds with the corollaries.
One comment I have is that the separation between this and the next section would be handled much better with subsections than a horizontal line.}

\vspace{5mm}
\noindent\rule{16.5cm}{0.4pt}
{\color{magenta} The rest of this seems technical. I'll pick it back up tomorrow morning.}

@@

	\caption{In the first line we act under an arc, so if another element without that arc is sent to that element, it must fix the arc as shown in the second line. In the third line we act to the right of an anchor, so if another element without that anchor is sent to that element, it must fix the anchor as shown in the fourth line. 
    {\color{magenta} This will be handled when we fully assemble the draft, but the figures should be made to fit the margins via adjustbox if possible}
  }
	%\label{Action}
\end{figure}

@@

\vspace{5mm}
\begin{lemma}
	Take a basis element $\beta\in W_{2n+r}^r$. Suppose the leftmost anchor in $\beta$ is at index $b$. Define $a_j$ such that $\beta(a_j)=a_{j-1}+1$ and $\beta(a_1)=1$ for all $j$ such that $a_j<b$.

@@

@@

	\vspace{5mm}
	To prove the inductive step for both (i) and (ii), we must split into cases:

	\begin{enumerate}
	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, and that $\exists s,t$ such that $s<i<t-1$, $s>1$ or $t<2n+r$, and $\beta(s)=t$. Also suppose the leftmost anchor is at some index $u>t$. Then we have a sub-matching $\beta(s,t)$, and by lemma 3.6 $E_\beta\subset Y_\beta$. Then, using corollary 3.2, the following equality holds:

@@

	\vspace{5mm}
	\item Suppose $\beta\in (1+T_i)W_{2n+r}^r$ for some $i$, the leftmost anchor is at a position $u>i+1$, and $\not\exists s,t$ such that $\beta(s)=t$ and $s<i<t-1$. Lemma $3.7$ characterizes all $\alpha\in E_\beta$. We would like to prove the following for arbitrary $q$ where $e>n+r$:

@@

	See figure 9 for an example of this equality.
	\\

	We will prove this equality through yet another inductive proof, this time inducting on the number of top level humps to the left of the rightmost anchor.

	Formally, as we have in earlier lemmas, we will define $a_j$ by $a_1:=\beta(1)$, $a_j:=\beta(a_{j-1}+1)$. Then $a_b=u$ for some $b>1$.

	\end{enumerate}
\end{proof}
